Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-10-29 paper/main.tex
fixing equation

\begin{equation}
  \label{eq:artist:construction:q:multifiber}
\begin{tikzcd}
  \dfiberc_a \arrow[rr, "\vchannelc"] \arrow[rd, "proj_a" description]          &            & \vfiberc_a \arrow[rr, "\vmarkd"]         &  & Im_{\vmarkdc} \subset \gtotalc \arrow[llld, "g_a" description, dashed]                  \\
 & \dfiberc_c &                                          &  &\\
  \dfiberc_b \arrow[rr, "\vchannelc^{\prime}"] \arrow[ru, "proj_b" description] &            & \vfiber_b \arrow[rr, "\vmarkd^{\prime}"] &  & Im_{\vmarkdc^{\prime}}\subset \gtotalc^{\prime} \arrow[lllu, "g_b" description, dashed]
  \end{tikzcd}
\end{equation}

>>>>

\begin{equation}
  \label{eq:artist:construction:q:multifiber}
\begin{tikzcd}
  \dfiberc_a \arrow[rr, "\vchannelc"] \arrow[rd, "proj_a" description]          &            & \vfiberc_a \arrow[rr, "\vmarkd"]         &  & Im_{\vmarkdc} \subset \gtotalc \arrow[llld, "g_a" description, dashed]                  \\
 & \dfiberc_c &                                          &  &\\
  \dfiberc_b \arrow[rr, "\vchannelc^{\prime}"] \arrow[ru, "proj_b" description] &            & \vfiberc_b \arrow[rr, "\vmarkd^{\prime}"] &  & Im_{\vmarkdc^{\prime}}\subset \gtotalc^{\prime} \arrow[lllu, "g_b" description, dashed]
  \end{tikzcd}
\end{equation}
